Git Learning Notes

### 2015-03-17 ch-intro/ch-intro.tex
post review step -2

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{blackbody1.pdf}
\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
\label{fig:introbb}
\end{figure}

@@

In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bonds reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b}

To fully use nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration processes. There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application.\cite{Wang2012}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{blackbody1.pdf}
\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius}]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
\label{fig:introbb}
\end{figure}

@@

In regarding to the contents of this study, electrochromic applications based on \gls{tmo} nanowires will benefit from the reduced diffusion depth by eliminating the deficiency of ions accumulation in amorphous oxide thin film devices, which in turn leads to shorter response time and higher coloration efficiency.\cite{Huang2008a,Scherer2012} And photocatalytic applications using \gls{tmo} nanostructures could harvest the huge surface area on which unsaturated bonds reside, thereby enabling a much higher efficiency.\cite{Mills1993,Merki2011,Chen2011b} To fully use nano-engineering, one must just be as aware of the limitations as one is of its advantages; for example, an obvious disadvantage is the difficulty of device fabrication using nanomaterials due to the size and requirements of new integration processes. There also exist some uncertainty as to the energy band modification present in nanostructures, which could be either useful or not depending on the application.\cite{Wang2012}

### 2015-03-17 ch-moox/moox.tex
post review step -2

% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
\caption[Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts. (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers. Insets show detailed features of different \ce{MoO3} structures.}
\label{fig:ch4sem2by3}
\end{figure}

@@

\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
\caption[Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
\label{fig:ch4ev}
\end{figure}
To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles. Small catalyst particles ranging from several hundred nanometers to several micrometers were found at different locations of these long 1D structures. As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, suggesting the particles were sodium molybdate catalysts.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
\label{fig:ch4edx1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
\caption[SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
\label{fig:ch4edx2}
\end{figure}
It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst. Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in this study were mostly found at the side wall of long nanobelts, and the location could be on the tip or several microns away from the tip. As for the microtowers, it was even rare to observe Na element. Some observations under similar controlled growth conditions was also listed as following to support the proposed growth model: 
\begin{enumerate}
\item When no Mo powder was used, NaOH still held onto substrate with some locations exhibiting etching.
\item 1 min growth show plates in high temperature end and irregular shapes in low temperature end.
\item 15 min growth show \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This was presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turned into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Some belt-like growth was visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increased to 10 $\mu$ m with prolonged growth.
\end{enumerate}

>>>>

% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_SEM_a.jpg}
\caption[Effect of alkali metal based catalysts on \ce{MoO3} depositions]{Effect of alkali metal based catalysts on the morphology of \ce{MoO3} depositions: (a) SEM image of rectangular nanoplates grown without catalysts. (b-f) SEM images of different morphologies grown with NaOH catalysts: (b) nanobelts grown on top of dense array of nanoplates,(c) close-up view of the forked nanoplates from an area indicated by the square in Fig.~\ref{fig:ch4sem2by3}, (d) long nanobelts, (e) side-view of ultra-long microbelts, and (f) side-view of microtowers. Insets show detailed features of different \ce{MoO3} structures.}
\label{fig:ch4sem2by3}
\end{figure}

@@

\caption[Raman shift of sodium molybdates and molybdenum oxide]{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{mooe_sem_ev}
\caption[Evolution of the second stage on \ce{MoO3} growth]{Growth evolution of the second stage of catalyst-assisted growth of \ce{MoO3} 1D structures: SEM images of the deposition at different growth temperatures with growth time of row 1: 15 min, row 2: 30 min, row 3: 60 min, and row 4: 90 min.}
\label{fig:ch4ev}
\end{figure}
To reveal the growth mechanisms for the long 1D structures in the second stage, specimens were carefully examined to locate the catalyst particles. Small catalyst particles ranging from several hundred nanometers to several micrometers were found at different locations of these long 1D structures. As shown in Fig.~\ref{fig:ch4edx1} and Fig.~\ref{fig:ch4edx2}, EDX element analysis confirmed the presence of Na, Mo, and O in these particles, suggesting the particles were sodium molybdate catalysts.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
\caption[Identifying the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
\label{fig:ch4edx1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX_tower}
\caption[Identifying the catalysts on the microtower structures]{SEM images and EDS spectra for identifying the location, morphology, and composition of the catalysts on the microtower structures: (a-b) a tiny catalyst particle (I) on top of a small cone shaped microtower (II), and (c-d) a catalyst particle (III) on a large and short microtower (IV).}
\label{fig:ch4edx2}
\end{figure}
It could be of difficulty to observe the sodium molybdate particles on the as-synthesized belts and towers due to the following two factors, one is the consumption of catalysts, such as evaporation; the other is the unpredictable location of the catalyst. Unlike the conventional \gls{vls} growth where the catalysts were predominantly found at the tip of 1D nanostructures, the catalyst in this study were mostly found at the side wall of long nanobelts, and the location could be on the tip or several microns away from the tip. As for the microtowers, it was even rare to observe Na element. Some observations under similar controlled growth conditions was also listed as following to support the proposed growth model: 
\begin{enumerate}
\item When no Mo powder was used, NaOH still held onto substrate with some locations exhibiting etching.
\item 1 min growth show plates in high temperature end and irregular shapes in low temperature end.
\item 15 min growth show \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This was presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turned into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Some belt-like growth was visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increased to 10 $\mu$ m with prolonged growth.
\end{enumerate}
